Embodied Neuromorphic Benchmarks

### 2015-08-13 paper/paper.tex
Added travis' comments/suggestions

Furthermore, neuromorphic hardware has another constraint that severely limits
the possibilities of simulation.  The normal approach when a simulation is
too simple to reflect reality is to add details to the simulation itself.
Incredibly finely detailed simulations can be created, filling in all of the
details needed.  However, accurate modelling of physical systems can very quickly
become \emph{impractical to run in realtime}.
This is a fundamental problem, in that most neuromorphic
hardware is about real-time interactions, and there is no way to slow down
the hardware to match the simulated environment.  This means that even if
we spent the considerable amount of research effort needed to define a
simulated environment for an embodied benchmark, running that simulation 
fast enough to interact with most of the desired hardware would require more
resources than are available.

@@

Given the success of this approach for evolutionary robotics, we propose
that it can be directly used for embodied neuromorphic benchmarks.  To do
this, we create software simulations for each benchmark task.  These simulations
must be fast enough to run in realtime (so that they can be controlled by
real neuromorphic hardware), and they must be extremely variable.  Each time
the simulation is run, different parameters will be chosed for this variability
(so one run might have a large degree of sensor noise while the next run has
none at all; one run might have more delay in the motor response and another
might have less power available).  Being successful at the benchmark means
being successful across all this variability.

@@

All of that said, we also need real physical embodiment as part of any
benchmark of this kind.  While we claim that reliable minimal simulations
are relatively easy to create, they are not a widely-used technique, and the
real proof of behaviour is always in the real world.  For this reason, we
also argue that every benchmark based on a minimal simulation should also
have an easy-to-construct physical analog.  However, this physical version
is not to be used as the primary benchmark.  Rather, this is meant as a
double-check that the system does actually behave as expected.

@@

To demonstrate this approach to creating embodied neuromorphic benchmarks,
we now consider a basic control task.  Suppose we have a system with a number
of joints $q$ and we want to send an output $u$ to those motors such that
the joints move to a particular desired position $q_d$.  Our only output is
the signal $u$ (one for each motor) and our only input is the current position
of each motor $q$.

@@

The standard solution to this problem is to add an I (integral) term ($K_i \int{(q_d-q) dt}$)
to the controller, making it a PID controller.  The idea here is that as the difference between where it is and
where we want it to be accumulates over time, the $K_i$ term gradually increases
how much extra force is being applied until it is large enough to counteract
the external force of gravity (or whatever other external forces are present).
However, this approach has great difficulty when $q_d$ changes, since the
external force due to gravity changes depending on the position of the arm $q$.
The controller ends up having to use the accumulated integral to ``relearn'' the
correct amount of extra force needed every time $q_d$ changes.

@@

Importantly, as pointed out by \cite{SannerSlotine1992} and \cite{Lewis1996}, rather than making explicit
assumptions about the exact functions that should be in $Y(q)$, we can use
a neural network approach where each neuron is a different function of $q$.  
As long as there is enough hetereogenetity (i.e. as long as the neural activity
forms a basis space that spans the desired space of functions), then the
learning rule will continue to work.  This approach has been used in the
Recurrent Error-driven Adaptive Control Hierarchy model of human motor control
(\citealt{dewolf2014}), and for quadcopter control [TODO: any citations for this?].

This then suggests an explicit neuromorphic benchmark.  The input to the
neuromorphic hardware is $q$, the system state.  This input is fed to each
neuron such that each neuron produces some output behaviour that is based on
this input.  Since $q$ will be multi-dimensional (if there is more than one
joint), we may give each neuron a random weighting of each $q$ value ($J_i=e_i \cdot q$, 
where $J_i$ is the input to neuron $i$, and $e_i$ is a randomly chosen vector\footnote{$e$ could also be chosen so as to regularly span the space of possibilities}).  Given this input, the neurons will produce some output $A$.
we now form a weighted sum of these outputs $Ad$, where $d$ is a matrix (number of neurons by number of elements in $q$)
that is initially all zeros.

@@

On top of this, we need to add the external force for which the adaptive system
is trying to compensate.  Rather than deciding on what specific external
force, we \emph{randomly generate} an equation controlling this force.  We start with a small set of
smooth functions on $X$ which are often found in dynamics equations ($x$, $x^2$,
$sin(x)$).  We then generate an external force of $Q (\zeta X(\beta q + \gamma) + \eta)$
where $\zeta$, $\beta$, $\gamma$, and $\eta$ are all randomly chosen fron $N(0,1)$
and $Q$ is a scaling factor to control how strong this external force is.  The
result is added to Equation 1.

@@

Of course, we need physical confirmation that the minimal simulation defined
in the previous section does a reasonable job.  For this, we define a
particular easy-to-build example of a system that can be usefully controlled
by this adaptive method.  In particular, we use the Lego Mindstorms EV3 robot kit.

The physical body is depicted in [TODO: add figure].  It consists of a single
motor, mounted in such a way that there is a significant amount of weight on
the arm itself (the weight of the motor itself).  Multiple motors can be
added, and other configurations can be considered and should also be suitable
for testing control, but here we just consider the basic case.

@@

- magnitude of nonlinearity $Q$

>>>>

Furthermore, neuromorphic hardware has another constraint that severely limits
the possibilities of simulation.  The normal approach when a simulation is
too simple to reflect reality is to add details to the simulation itself.
Incredibly finely detailed simulations can be created, filling in all of the
details needed.  However, accurate modelling of physical systems can very quickly
become \emph{impractical to run in real time}.
This is a fundamental problem, in that most neuromorphic
hardware is about real-time interactions, and there is no way to slow down
the hardware to match the simulated environment.  This means that even if
we spent the considerable amount of research effort needed to define a
simulated environment for an embodied benchmark, running that simulation 
fast enough to interact with most of the desired hardware would require more
resources than are available.

@@

\subsection{Minimal Simulation as a Benchmark}

Given the success of this approach for evolutionary robotics, we propose
using a minimal simulation as a neuromorphic benchmark.  First, we note that
one important use of a benchmark is that by knowing how well particular
hardware performs on that benchmark, you can reasonably infer how well
that hardware will perform in other situations.  For example, if an image recognition
algorithm performs well on the MNIST hand-written digit recognition
benchmark, we can use that knowledge to guess that it may also perform well on
a different recognition task.  Of course, this inference will fail if that
algorithn has been specifically over-fit to exactly that one situtation.  For
that reason, it would be useful to have a benchmark that covers a large range
of variations on the task.  If the hardware performs well across that
variability, then it is more likely to also work in whatever new situation we
want to use it in.

To achieve this, we need software simulations of the environment for the task.
These simulations
must be fast enough to run in real time (so that they can be controlled by
real neuromorphic hardware), and they must be extremely variable.  Each time
the simulation is run, different parameters will be chosed for this variability
(so one run might have a large degree of sensor noise while the next run has
none at all; one run might have more delay in the motor response and another
might have less power available).  Being successful at the benchmark means
being successful across all this variability.

@@

The minimal simulation described above forms the core of our benchmark.
However, the point of that benchmark is that is should do a reasonable job
of generalizing to real-world physical tasks.  It is then useful to
supplement that simulation benchmark with at least one easy-to-construct 
physical analog.  This physical version would be one particular instance of the
type of situation the benchmark is meant to cover.  For that reason, it
is much more restrictive in terms of what general conclusions can be drawn
from how well different hardware performs in that situation.  Rather, it is
gives an explicit and understandable double-check that models that perform
well on the simulation benchmark also perform well in a physical environment.
Even considering the advantages of benchmarking using minimal simulations,
it is still useful to have a real physical point of comparison as well.

@@

To demonstrate this approach to creating embodied neuromorphic benchmarks,
we now consider a basic control task.  Suppose we have a system with a number
of joints $q$ and we want to send an output $u$ to those motors such that
the joints move to a particular desired position $q_d$.  Our only output is
the signal $u$ (one for each motor) and our only inputs are the current position
of each motor $q$ and the desired positions $q_d$.

@@

The standard solution to this problem is to add an I (integral) term ($K_i \int{(q_d-q) dt}$)
to the controller, making it a PID controller.  The idea here is that as the difference between where it is and
where we want it to be accumulates over time, the $K_i$ term gradually increases
how much extra force is being applied until it is large enough to counteract
the external force of gravity (or whatever other external forces are present).
However, this approach has great difficulty when $q_d$ changes, since the
external force due to gravity changes depending on the position of the arm $q$.
The controller ends up having to ``relearn'' the
correct amount of extra force needed every time $q_d$ changes.

@@

Importantly, as pointed out by \cite{SannerSlotine1992} and \cite{Lewis1996}, rather than making explicit
assumptions about the exact functions that should be in $Y(q)$, we can use
a neural network approach where each neuron is a different function of $q$.  
As long as there is enough hetereogenetity (i.e. as long as the neural activity
forms a basis space that is capable of approximating the external forces), then the
learning rule will continue to work.  This approach has been extended to
biologically plausible neurons and been used in both the
Recurrent Error-driven Adaptive Control Hierarchy model of human motor control
(\citealt{dewolf2014}) and quadcopter control (\citealt{KomerThesis}).

This then suggests an explicit neuromorphic benchmark.  The input to the
neuromorphic hardware is $q$, the system state.  This input is fed to each
neuron such that each neuron produces some output behaviour that is based on
this input.  Since $q$ will be multi-dimensional (if there is more than one
joint), we may give each neuron a random weighting of each $q$ value ($J_i=e_i \cdot q$, 
where $J_i$ is the input to neuron $i$, and $e_i$ is a randomly chosen vector\footnote{$e$ could also be chosen so as to regularly span the space of possibilities}).  Given this input, the neurons will produce some output $A$.
We now form a weighted sum of these outputs $Ad$, where $d$ is a matrix (number of neurons by number of elements in $q$)
that is initially all zeros.

@@

On top of this, we need to add an external perturbing force.  In a real system,
this could be the effects of gravity given the current configuration of the
motors, or of other unexpected influences.  
Rather than chosing one particular fixed external force for our benchmark,
we \emph{randomly generate} this force each time the benchmark is run.

We start with a small set of
smooth functions $f$ which are often found in dynamics equations (e.g. $x$, $x^2$,
$sin(x)$).  We then generate an external force of $K_f (\zeta \cdot f(\beta \cdot q + \gamma) + \eta)$
where $\zeta$, $\beta$, $\gamma$, and $\eta$ are all random vectors and
$K_f$ is a scaling factor to control how strong this external force is.  The
result is added to Equation 1.  Note that this means that if $q$ is 4-dimensional
(i.e. if there are four joints being controlled) and if there are three smooth
functions in $f$ (as there are here), then $\beta$, $\gamma$, and $\eta$ are 
all vectors of length 4 and $\zeta$ is a 4x12 matrix.  All of these values are
randomly chosen from the normal distribution $N(0,1)$.

@@

Of course, we also want an indication that the minimal simulation defined
in the previous section is reasonably representative of the sorts of real-world
situations in which we might want to use these controllers.  Importantly, 
this physical instantiation does not have to exactly match one particular
parameter setting of the minimal simulation.  Rather, we want a physical system
that shares basic functional similarities to the minimal simulation defined
previously.

For example, we want the inputs to the system to act like $u$, in that a
positive number will increase some velocity $v$ which will in turn increase some
sensor value $q$.  We want there to be some sort of external force applied that
affects $q$, and we want that external force itself to be a function of $q$.
We want there to be communication delays and noise in the sensory and motor
system, and we want all of these effects to be somewhere within the extreme
ranges covered by the minimal simulation.  While this cannot prove that hardware
that is successful in simulation will always be successful in any similar
real-world task, it at least gives an existence proof that there is at least
one real-world task where it also performs reasonably.

For this demonstration, we define an easy-to-build example of a system that can be usefully controlled
by this adaptive method.  In particular, we use the Lego Mindstorms EV3 robot kit,
organized as shown in [TODO: add figure].  It consists of a single
motor, mounted in such a way that there is a significant amount of weight on
the arm itself (the weight of the motor itself).  Multiple motors can be
added, and other configurations can be considered and should also be suitable
for testing control, but here we just consider the basic case.

@@

- magnitude of nonlinearity $K_f$
